COVID Shutdown Regulations Negatively Impact Employment and Sales of Restaurants in Ontario

### 2021-02-26 outputs/paper/paper.Rmd
Commit for data discussion

@@

>>>>

always_allow_html: yes

@@

```{r}
data.frame(table(simulated_dataset$q14_loans,simulated_dataset$q1_city))%>%
  mutate(Var1 = fct_relevel(Var1 ,"Prefer not to say","More than $50,000","$40,000 ~ $50,000","$20,000 ~ $40,000","$0 ~ $20,000")) %>% 
  ggplot(aes(Var1, Freq,fill=Var2)) +
  geom_bar(stat = "identity", width = 0.8, position = position_dodge())+
  ylab("Number of responses")+
  xlab("Grant value")+
  ggtitle("How much loans have you applied for the COVID-19 related reasons?")+
  guides(fill=guide_legend(title="City"))+
  theme_minimal()+
  theme(axis.text.x = element_text(angle = 0))+
  coord_flip()

```
As shown in figure 15, Peterborough restaurants have received more business loans than restaurants in Brantford. Since loans have to be paid back, businesses operating at low operating expectation are less likely to apply for the loans. And this corresponds with our previous findings of the expected survival time (Figure \@ref(fig:q8)) and expected recovery time (Figure \@ref(fig:q10)) as mentioned before.

**They probably see a brighter future for their business to think out their repayments accordingly. However, Brantford restaurants which according to figure 8 are less hopeful to their business in future, probably mutter “It is never too late to mend” and refrain adding to their liabilities, though the loan’s interest be very low.**
